\Large The state learner -- a super learner for right-censored data

### 2024-05-27 tex/journal-version/manuscript.tex
readme update

In this section we use the prostate cancer data of
\cite{kattan2000pretreatment} to illustrate the use of the state
learner in the presence of competing risks. We have introduced the
data in Section~\ref{sec:numer-exper}. The data consists of 1,042
patients who are followed from start of followup until tumor
recurrence, death without tumor recurrence or end of followup
(censored) whatever came first. For the sole purpose of illustration,
we estimate the average treatment effect of hormone therapy on death
and tumor recurrence. To do this we adapt the estimation strategy of
Section~\ref{sec:targeted-learning} as follows. We use the state
learner to rank libraries of learners for the cause-specific
cumulative hazard functions of tumor recurrence, death without tumor
recurrence, and censoring.  The libraries of learners each include
five learners: a Nelson-Aalen, three Cox regression models
(unpenalized, Lasso, Elastic net) each including additive effects of
the 5 covariates (Section~\ref{sec:numer-exper}), and a random
survival forest. We use the same set of learners to learn the
cumulative hazard function of tumor recurrence \( \Lambda_1 \), the
cumulative hazard function of death without tumor recurrence
\( \Lambda_2 \), and the cumulative hazard function of the conditional
censoring distribution $\Gamma$.  We then use the highest ranked
combination of learners and apply
formula~\eqref{eq:one-step-comp-ate}.

>>>>

In this section we use the prostate cancer data of
\cite{kattan2000pretreatment} to illustrate the use of the state
learner in the presence of competing risks. We have introduced the
data in Section~\ref{sec:numer-exper}. The data consists of 1,042
patients who are followed from start of followup until tumor
recurrence, death without tumor recurrence or end of followup
(censored) whatever came first. For the sole purpose of illustration,
we estimate the average treatment effect of hormone therapy on death
and tumor recurrence. To do this we adapt the estimation strategy of
Section~\ref{sec:targeted-learning} as follows. We use the state
learner to rank libraries of learners for the cause-specific
cumulative hazard functions of tumor recurrence, death without tumor
recurrence, and censoring.  The libraries of learners each include
five learners: the Nelson-Aalen estimator, three Cox regression models
(unpenalized, Lasso, Elastic net) each including additive effects of
the 5 covariates (Section~\ref{sec:numer-exper}), and a random
survival forest. We use the same set of learners to learn the
cumulative hazard function of tumor recurrence \( \Lambda_1 \), the
cumulative hazard function of death without tumor recurrence
\( \Lambda_2 \), and the cumulative hazard function of the conditional
censoring distribution $\Gamma$.  We then use the highest ranked
combination of learners and apply
formula~\eqref{eq:one-step-comp-ate}.
